### 2019-09-26 ThesisJo/2_background.tex
2019-09-17

Consider a sonar imaging scenario where an encoded signal is transmitted to highlight a surface of interest, and assume that the backscattered wavefield is properly sampled using a uniform linear array of receivers. After stripping the carrier frequency by heterodyning and the signal signature by  matched filtering (Fig. \ref{I_beamforming}), an image is formed by coherently combining the receiver outputs to focus at one angle (or point) at a time. The principle of adjusting the array's focus in range and direction is commonly referred to as beamforming, and involves assigning suitable delays and weights to the array's channels.

@@

Imagine we record a wavefield with $M$ sensors arranged in a uniformly spaced linear array (ULA) and attach a reference frame $\ubar{A} \triangleq (\udot{A},\uvec{A})$ to it, where $\udot{A}\in\mathbb{A}$ is its absolute position and $\uvec{A}\triangleq\big(\hat{x}_{A},\hat{y}_{A},\hat{z}_{A}\big)\in\mathbb{V}^3$ its absolute orientation (where $\hat{\cdot}$ denotes unit length). Assume that the array channels are digitally delayed to focus at a pixel with azimuth angle $\theta$ and range sample $n$, such that the delayed data from the $m$th channel can be expressed as $x_m[\theta,n-\Delta_m]\in\mathbb{C}$. By making the dependence on $\theta$ implicit and assuming the data to be pre-delayed to the pixel of interest, we can simply the notation to $x_m[\theta,n-\Delta_m] = x_m[n]$.

>>>>

Consider an acoustic signal transmitted to highlight a surface of interest. Assume the backscattered wavefield is properly sampled using a uniform linear array (ULA) of receivers. After stripping the carrier frequency by heterodyning and the signal signature by matched filtering (Fig. \ref{I_beamforming}), an image is formed by coherently combining the receiver outputs to focus at one angle (or point) at a time. The principle of adjusting the array's focus in range and direction is commonly referred to as beamforming, and involves assigning suitable delays and weights to the array's channels.

@@

Imagine an array with $M$ sensors with a reference frame $\ubar{A} \triangleq (\udot{A},\uvec{A})$ attached to it, where $\udot{A}\in\mathbb{A}$ is its absolute position and $\uvec{A}\triangleq\big(\hat{x}_{A},\hat{y}_{A},\hat{z}_{A}\big)\in\mathbb{V}^3$ its absolute orientation (where $\hat{\cdot}$ denotes unit length). Assume that the array channels are digitally delayed to focus at a pixel with azimuth angle $\theta$ and range sample $n$, such that the delayed data from the $m$th channel can be expressed as $x_m[\theta,n-\Delta_m]\in\mathbb{C}$. By making the dependence on $\theta$ implicit and assuming the data to be pre-delayed to the pixel of interest, we can simply the notation to $x_m[\theta,n-\Delta_m] = x_m[n]$.

### 2019-09-26 ThesisJo/3_publications.tex
2019-09-17

@@

%\begin{itemize}\setlength\baselineskip{0pt}
%\item \emph{Optimization method}, or criteria for adaptiveness and constraints;
%\item \emph{Solution space}, or range of possible values for an optimization problem that satisfy a problem's constraints;
%\item \emph{Domain}, or data representation, 
%\item \emph{Application}, 
%\item \emph{Computational complexity}, $O(N^3)$.
%\item Hardware acceleration. 
%\item Information significance: Minimal temporal sample support (~single snapshot)
%\end{itemize}
%
%All:
%- GPU

>>>>

\begin{figure}[tp]
\makebox[\linewidth][c]{%
\graphicsAI[drawing,width=1.3\linewidth]{gfx/article_relation.svg}}
\caption{Article relations. The first three articles reconstructs images from acoustic echoes. The last article synthesizes image templates from 3D models and object parameters estimated from the reconstructed image. The two key traits are: accelerated adaptivity.  }
\end{figure}

@@

%\begin{itemize}\setlength\baselineskip{0pt}
%\item \emph{Optimization method}, or criteria for adaptiveness and constraints;
%\item \emph{Solution space}, or range of possible values for an optimization problem that satisfy a problem's constraints;
%\item \emph{Domain}, or data representation, 
%\item \emph{Application}, 
%\item \emph{Computational complexity}, $O(N^3)$.
%\item Hardware acceleration. 
%\item Information significance: Minimal temporal sample support (~single snapshot)
%\end{itemize}
%
%All:
%- GPU
% MVDR: Needs acceleration
% LCA: No particular need of acceleration
% Sim: Needs acceleration
